Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2023-02-06 tex/sections/apm.tex
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Assume that we have a complex component which has a considerable arithmetic circuit complexity. If this component
is needed in some arbitrary computation steps, we will need to repeat its circuit in every step of the computation. This
will increase the complexity of proof generation considerably. Fortunately, there is a workaround. Instead of
repeating the circuit of the component, we can use a simpler cryptographic accumulator circuit during the
computation, and use a final verification circuit at the end to verify the functionality of the component.

@@

Now the prover needs to prove that he knows values $in_1,out_1,\dots,in_k,out_k$ such that they are correctly
produced by the component:
\[
    f((in_1,\dots,in_k)) = (out_1,\dots,out_k)
\]
and their digest is also correct:
\[
    h(in_1,out_1,\dots,in_k,out_k) = digest_f
\]
where $f$ and $digest_f$ are known to the prover and verifier.

@@

Interestingly, this approach can reduce the number of computation steps as well. When we use an accumulator circuit
instead of the component, $out$ can be available in the same computation step that $in$ is available. This will
eliminate the computation step that is needed for generating $out$ by the component's circuit.

>>>>

Assume that we have a component which has a considerable arithmetic circuit complexity. If this complex component
is needed in some arbitrary computation steps, we will need to repeat its circuit in every step of the computation. This
will increase the complexity of proof generation considerably. Fortunately, there is a workaround. Instead of
repeating the circuit of the component, we can use a simpler cryptographic accumulator circuit during the
computation, and use a final verification circuit at the end to verify the functionality of the component.

@@

Now the prover needs to prove that he knows values $in_1,out_1,\dots,in_k,out_k$ such that they are correctly
produced by the component:
\[
    f((in_1,\dots,in_k)) = (out_1,\dots,out_k)
\]
and their digest is also correct:
\[
    h(in_1,out_1,\dots,in_k,out_k) = digest_f
\]
where $f$ is known to both the prover and verifier.

@@

Interestingly, this approach can reduce the number of computation steps as well. When we use an accumulator circuit
instead of the component, $out$ will be available in the same computation step that $in$ is available. This will
eliminate the computation step that is needed for generating $out$ by our component's circuit.
